Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-24 paper.tex
Updated Experiments
Second experiment.

>>>>

            As our second experiment to further validate and prove our
            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_bohachevsky5} and
            Table~\ref{tab.fun_bohachevsky10} (for five and ten dimensions,
            respectively). Due to the observation and analysis of these
            results, we identify our proposed strategy obtained solutions in
            the same order as the traditional Xover Mutation, in a
            significantly reduced number of evaluations.
